P2P-LLM: Collaborative LLM Inference

### 2025-05-01 docs/paper/main.tex
paper outline

\documentclass[twoside,11pt]{article}

@@

\usepackage{lastpage}
\jmlrheading{23}{2022}{1-\pageref{LastPage}}{1/21; Revised 5/22}{9/22}{21-0000}{Author One and Author Two}

@@

\ShortHeadings{Sample JMLR Paper}{One and Two}
\firstpageno{1}

@@

\title{Sample JMLR Paper}

\author{\name Author One \email one@stat.washington.edu \\
	\addr Department of Statistics\\
	University of Washington\\
	Seattle, WA 98195-4322, USA
	\AND
	\name Author Two \email two@cs.berkeley.edu \\
	\addr Division of Computer Science\\
	University of California\\
	Berkeley, CA 94720-1776, USA}

\editor{My editor}

@@

\begin{keywords}
	keyword one, keyword two, keyword three
\end{keywords}

@@

\blindmathpaper

@@

% Acknowledgements and Disclosure of Funding should go at the end, before appendices and references

\acks{All acknowledgements go at the end of the paper before appendices and references.
	Moreover, you are required to declare funding (financial activities supporting the
	submitted work) and competing interests (related financial activities outside the submitted work).
	More information about this disclosure can be found on the JMLR website.}

@@

\appendix
\section{}
\label{app:theorem}

% Note: in this sample, the section number is hard-coded in. Following
% proper LaTeX conventions, it should properly be coded as a reference:

%In this appendix we prove the following theorem from
%Section~\ref{sec:textree-generalization}:

In this appendix we prove the following theorem from
Section~6.2:

\noindent
{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
respective empirical mutual information values based on the sample
$\dataset$. Then
\[
	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
\]
with equality only if $u$ is identically 0.} \hfill\BlackBox

\section{}

\noindent
{\bf Proof}. We use the notation:
\[
	P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
	P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
\]
These values represent the (empirical) probabilities of $v$
taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\

{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}

>>>>

\documentclass[preprint,twoside,11pt]{article}

@@

\usepackage{lastpage}
\jmlrheading{23}{2022}{1}{1/21}{9/22}{21-0000}{Author One and Author Two}

@@

@@

\title{P2P-LLM: Collaborative LLM Inference}

\author{\name Andrew Boessen \email boessena@bc.edu \\
}

@@

@@

\section{Realted Work}

\subsection{Crowd Computing}

\subsection{P2P Networks}

\section{Peer-to-Peer Network}

\subsection{Path Finding}

\subsection{Revenue Optimization}

\subsection{Network Equilibrium}

\subsection{Strategy-Proofness}

\section{Blockchain}

\subsection{Contracts}

\section{Results}

@@

@@

\appendix
\section{}
